A novel catalyitic model for estimating age-specific measles sero-prevalence uisng case-incidence data: a case study from the Democratic Republic of the Congo

### 2018-06-22 Paper/paper.tex

There was high variability in the estimated vaccine effectiveness in the 11 provinces.  In 8 of 11 provinces, the fitted values are considerably lower than the conventionally assumed vaccine efficacy of ~85\% for measles vaccine~\cite{Uzicanin2011}. Based on the results from the simulation study, above, the absolute value of these estimates should be taken with caution; however, they may reflect a qualitative ranking of effectiveness, or the reliability of vaccination survey responses in these provinces.  The 4 provinces with the lowest values, Bandundu, Sud Kivu, Kasai Occidental, and Kasai Orientale, all reported relatively high vaccination coverage in the 2014 DHS relative to the seroprevalence.  Thus, low effectiveness is consistent with this observation.  Notably, this is corroborated by low estimated effectiveness when the model is analyzed in the absence of serological data  (Fig.~\ref{fig:foivaccveff}(c)).

>>>>

When the model was fit using only the age-specific case incidence and vacciantion coverage survey data, the estiamted vaccination effectiveness was fairly uniform for all provinces, and did not move far from the prior value (Fig.~\ref{fig:foivaccveff}(c)).  This is consistent with the results from the simulation study and suggests that there is insufficient information in the case and vacciantion data alone to indentify this parameter.  However, when the model was fit, including the DHS serology survey among children from 6-59 months of age, there was high variability in the estimated vaccine effectiveness in the 11 provinces.  In 8 of 11 provinces, the fitted values are considerably lower than the conventionally assumed vaccine efficacy of ~85\% for measles vaccine~\cite{Uzicanin2011}. Based on the results from the simulation study, above, the absolute value of these estimates should be taken with caution; however, they may reflect a qualitative ranking of effectiveness, or the reliability of vaccination survey responses in these provinces.  The 4 provinces with the lowest values, Bandundu, Sud Kivu, Kasai Occidental, and Kasai Orientale, all reported relatively high vaccination coverage in the 2014 DHS relative to the seroprevalence.  Thus, low effectiveness is consistent with this observation.  Notably, this is corroborated by low estimated effectiveness when the model is analyzed in the absence of serological data  (Fig.~\ref{fig:foivaccveff}(c)).
